Exponential Integrals\\ [1ex]

### 2022-03-21 draft2.tex
Edit section on Puiseux series property

However, if $f(z)=\sum_{n\geq 0}a_nz^{-n}$ is a Gevrey-$1$ series, then the Borel transform of $\mathcal{B}(z^{-\alpha}f)(\zeta)$ is a germ of meromorphic function at the oringin: indeed 
\begin{align*}
\mathcal{B}(z^{\alpha}f)(\zeta)&=\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}\ast\left(a_0\delta+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)\\
&=a_0\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}+\sum_{n\geq 0}a_{n+1}\frac{\zeta^{n+\alpha}}{\Gamma(1+n+\alpha)}
\end{align*}

In particular, if $\alpha\in (1,+\infty)$, then $\mathcal{B}(z^{\alpha}f)(\zeta)$ is actually a germ of holomorphic functions on the Riemann surface of $\zeta
^{\alpha-1}$, otherwise if $\alpha\in (-\infty,1)$ then $\mathcal{B}(z^{\alpha}f)(\zeta)$ is a meromorphic functions on the Riemann surface where $\zeta^{\alpha-1}$ defines an analytic coordinate. The case of interest for usa in the following is when $\alpha=\tfrac{1}{2}$, hence if $a_0\neq 0$, the Borel trasform will be merorphic at the origin and definied on the Riemann surface of the square root.

\subsubsection{Properties of the Borel transform}
We now recall some properties of the Borel transform: let $f(z)=\sum_{n\geq 0}a_nz^{-n}$ and denote by $\hat{f}(\zeta)\defeq\mathcal{B}(f(z))$

>>>>

However, if $f(z)=\sum_{n\geq 0}a_nz^{-n}$ is a Gevrey-$1$ series, and $\alpha$ is a rational number with denominator $q$, then $\mathcal{B}(z^{-\alpha}f)(\zeta)$ is a germ of meromorphic function at the oringin of the Riemann surface of $\zeta^{1/q}$. Indeed,
\begin{align*}
\mathcal{B}(z^{-\alpha}f)(\zeta)&=\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}\ast\left(a_0\delta+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)\\
&=a_0\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}+\sum_{n\geq 0}a_{n+1}\frac{\zeta^{n+\alpha}}{\Gamma(1+n+\alpha)}.
\end{align*}
If $\alpha > 1$, then $\mathcal{B}(z^{-\alpha}f)(\zeta)$ is actually a germ of holomorphic functions on the Riemann surface of $\zeta
^{1/q}$. We're interested in the case where $\alpha=\tfrac{1}{2}$, so the Borel transform is meromorphic on the Riemann surface of $\zeta^{1/2}$, and has a pole at $\zeta = 0$ unless $a_0 = 0$.
\subsubsection{Properties of the Borel transform}
We now recall some properties of the Borel transform: let $f(z)=\sum_{n\geq 0}a_nz^{-n}$ and denote by $\hat{f}(\zeta)\defeq\mathcal{B}(f(z))$
